A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-24 sections/Related.tex
RW

@@

\jimmy{Guarded Impredicative}

\jimmy{Dunfield's new work}

>>>>

\jimmy{Dunfield's new work}
DK's algorithm is shown to be sound, complete and decidable with 70 pages of manual proofs.
Though carefully written, some of the proofs are incorrect,
thus we find it difficult to formalize in a proof assistant.
Their follow-up work~\cite{} enriches the bidirectional higher-rank system with
existentials and indexed types.
With a more complex declarative system, they developed a proof of over 150 pages.
It is even more difficult to argue its correctness for every single detail within such a big development.
Unfortunately, we find its Lemma 26 (Parallel Admissibility) has the same issue with
a lemma of the same name in their previous work, which has a false conclusion.

@@

\jimmy{Guarded Impredicative}
A recent work proposed Guarded Impredicative Polymorphism~\cite{},
as an improvement on GHC's type inference algorithm with impredicative instantiation.
They make use of local informations in $n$-ary applications to
infer polymorphic instantiations with a relatively simple specification and unification algorithm.
Although not all impredicative instantiation can be handled perfectly,
their algorithm is already practically useful.
Unfortunately, no mechanical formalization is provided for this work.

\paragraph{Formalizations of Type-Inference Algorithms}
Since the publication of the {\sc POPLMark} challenge~\cite{aydemir2005mechanized},
many theorem provers and packages provide new methods for dealing
with variable binding~\cite{aydemir2008engineering,urban2008nominalTech,chlipala2008parametric},
and more and more type systems are formalized with these tools.
However, mechanising algorithmic aspects, like unification and
constraint solving, have received very little attention and is still challenging.
Moreover, while most tools supports local (input) contexts in a neat way, which have a simple
binding and scoping structure, many practical type-inference algorithms require
more complex binding structures with output contexts or various form of constraint solving procedure.

Algorithm $\mathcal{W}$,
as one of the classic type inference algorithms for polymorphic type systems,
has been manually proven to be sound and complete
with respect to the Hindley-Milner type system~\cite{}.
After around 15 years, the algorithm is foramlly verified by
Naraschewski and Nipkow~\cite{naraschewski1999type} in Isabelle/HOL~\cite{nipkow2002isabelle}.
The treatment of new variables is tricky at that time, while the overall structure follow the
structure of Damas's manual proof closely.
%Another complication is the encoding of substitutions,
%which they chose to formalize as a function instead of an association list.
Later on, other researchers~\cite{dubois2000proving,dubois1999certification}
formalized algorithm $\mathcal{W}$ in Coq~\cite{Coq}.
Nominal techniques~\cite{urban2008nominalTech} in Isabelle/HOL have been
developed to help programming language formalizations, and are used for a similar
verification~\cite{urban2008nominal}. Moreover, Garrigue~\cite{garrigue2015certified}
mechanized a type inference algorithm,
with the help of locally nameless cofinite quantification~\cite{},
for Core ML extended with structural polymorphism and recursion.
